Supporting Information

### 2021-10-21 Asymptomatic_LSR_Supplement_noPrisma_yesROB_HI.Rmd
update

rob_records$authoryear <- paste0(rob_records$author_1, " (", rob_records$year, ")")
rob_records <- rob_records[rob_records$record_id < "5566", ]

>>>>

rob_records$authoryear <- paste0(rob_records$author_1, " (", rob_records$year, ")")
#rob_records <- rob_records[rob_records$record_id < "5566", ]
rob_records <- rob_records[rob_records$record_id < "5296", ]
